---
title: "R Notebook"
output: html_notebook
---
```{r}
library("ggplot2")
```
#Setting up data for CD4_pct
```{r}
#Fixing the CD69 data that Genevieve gave me
#empty strings need to be filled with NA
CD69df = read.csv("~/my.work/PhD/HomestaticExpansionProject/T cell Activation Summary_Jon.csv", header = FALSE, na.strings=c("","NA"))
#has a weird first row with one entry saying "CD69.Data.Summary", so I'm removing it, and the row with names
CD69df = CD69df[-(1:2),]
#Removing an empty column
CD69df[[15]] = NULL
# Using actual Column names now
colnames(CD69df) <- c("PerformedBy", "Date", "Notebook", "Page", "Mouse Tag",
                      "TissuesUsed", "TubeNumbers", "Genotype", "Age", "Notes", 
                      "CD4_pct", "CD8_pct", "CD4CD69_pct", "CD8CD69_pct",
                      "CD4CD44CD62L_pct", "CD8CD44CD62L_pct")

#Now removing the rows that have empty data under the CD4_pct column
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
CD69df = completeFun(CD69df, "CD4_pct")
# Numbers aren't being read as numeric because the first lines are messed up
cl4 = which( colnames(CD69df)=="CD4_pct" )
CD69df[cl4:ncol(CD69df)] = lapply(CD69df[cl4:ncol(CD69df)], as.character)
CD69df[cl4:ncol(CD69df)] = lapply(CD69df[cl4:ncol(CD69df)], as.numeric)

#Age seems to have a problem, it read age 4 as the highest when I made a plot
CD69df["Age"] = lapply(CD69df["Age"], as.character)
CD69df["Age"] = lapply(CD69df["Age"], as.numeric)


# Replacing the IL-2 HET with WT
CD69df$Genotype[CD69df$Genotype == "IL-2-HET"] = "WT"

```
#Plotting Genevieves results
```{r}
ggplot(data=CD69df, aes(x=Age, y=CD4CD69_pct)) +
  geom_point(position = position_dodge(width = 0.8), aes(color = Genotype))

#####################
#Now with Error Bars#
#####################
#Guide I am using - http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/
#Now to get the error bars
library("Rmisc")
cd4cd69 <- summarySE(CD69df, measurevar="CD4CD69_pct", groupvars=c("Age","Genotype"))
#Replacing the NA's produced by day 1's
cd4cd69[is.na(cd4cd69)] = 0

#Positional Dodge
pd <- position_dodge(0.1)

ggplot(cd4cd69, aes(x=Age, y=CD4CD69_pct, colour=Genotype, group=Genotype)) + 
    geom_errorbar(aes(ymin=CD4CD69_pct-sd, ymax=CD4CD69_pct+sd), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "CD4CD69+ Percent sdbar")

ggplot(cd4cd69, aes(x=Age, y=CD4CD69_pct, colour=Genotype, group=Genotype)) + 
  geom_errorbar(aes(ymin=CD4CD69_pct-se, ymax=CD4CD69_pct+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Percentage of CD4CD69+ T cells sebar", y = "Percent", x = "Age in Days")+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=18,face="bold"),
        plot.title = element_text( size = 20, face = "bold")
        )

#Total Cell numbers with Error bars
CD4ct <- summarySE(pop, measurevar="CD4CT", groupvars=c("Age","Genotype"))
#Replacing the NA's produced by day 1's
CD4ct[is.na(CD4ct)] = 0

ggplot(CD4ct, aes(x=Age, y=CD4CT, colour=Genotype, group=Genotype)) + 
  geom_errorbar(aes(ymin=CD4CT-se, ymax=CD4CT+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Total CD4 T Cells in the 10^6 with SE bars", y = "Counts", x = "Age in Days") + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=18,face="bold"),
        plot.title = element_text( size = 20, face = "bold")
        )



```
#Plotting CD62L
```{r}
colnames(CD69df)
ggplot(data=CD69df, aes(x=Age, y=CD4CD44CD62L_pct)) +
  geom_point(position = position_dodge(width = 0.8), aes(color = Genotype), size = 3)+
  labs(title = "CD4CD44CD62L+ Percentage")

```

#Getting Treg data for Genevieve
```{r}
############################################################
#
# Getting Treg data for Genevieve
#
############################################################
library("dplyr")

popSpleen = subset(pop, Organ == 'Spleen')
#Desired columns 1:18, "CD4Ratio", "X4TregRatio", "CD4CT", "X4TregCT"
colNumbers = match(c("CD4Ratio", "X4TregRatio", "CD4CT", "X4TregCT"),names(pop))
colNumbers
popCD4nTregs = popSpleen[c[1:18, 45, 49, 58, 62]]
popCD4nTregs = popSpleen[,c[45, 49, 58, 62,1:18]]

popCD4nTregs = dplyr::select(popSpleen, 1:18, colNumbers)
colnames(popCD4nTregs)
write.csv(popCD4nTregs, "~/my.work/PhD/Homestatic Expansion Project/Code/Rscripts/temp/TregDataForGenevieve.csv")
```
#Plotting thymus weight

```{r}
popThym = subset(pop, Organ == "Thymus")
popThym$OrganWeight = popThym$OrganWeight * 10**3
ggplot(popThym, aes(x=Age, y=OrganWeight, colour=Genotype, group=Genotype)) + 
  geom_point(size=3)+
  labs(title = "Thymus Size", 
       y = "Weight in miligrams")
```

#Regression Analysis of WT vs KO in CD69 data
```{r}
CD69WT = subset(CD69df, Genotype == "WT")
CD69KO = subset(CD69df, Genotype == "IL-2-KO")

reg69WT = lm(formula = CD4CD69_pct ~ Age, data = CD69WT)
reg69KO = lm(formula = CD4CD69_pct ~ Age, data = CD69KO)
summary(reg69WT)
#-0.7105, 0.1703
summary(reg69KO)
#0.5976, 0.5358
#Calculating Z score (sl1 - sl2)/sqrt(SE1**2 + SE2**2)
(-0.7105 - 0.5976) / sqrt(0.1703**2 + 0.5358**2)
#Z = -2.326697
#P = 0.010009
```

```{r}
WTregr = summary(lm(CD4CD69_pct ~ poly(Age,4, raw = TRUE), data = CD69WT))
KOregr = summary(lm(CD4CD69_pct ~ poly(Age,4, raw = TRUE), data = CD69KO))
WTregr
KOregr
```

```{r}
#Link of how
#https://stackoverflow.com/questions/23334360/plot-polynomial-regression-curve-in-r
fit <- lm(CD4CD69_pct ~ poly(Age,4), data = CD69WT)
plot(CD69WT$CD4CD69_pct ~ CD69WT$Age, main = "WT")
lines(sort(CD69WT$Age), fitted(fit)[order(CD69WT$Age)], col='red', pch=20)

fit <- lm(CD4CD69_pct ~ poly(Age,4), data = CD69KO)
plot(CD69KO$CD4CD69_pct ~ CD69KO$Age, main = "KO")
lines(sort(CD69KO$Age), fitted(fit)[order(CD69KO$Age)], col='red', pch=20)
```

```{r}
lm(CD69WT$CD4CD69_pct ~ poly(CD69WT$Age,2))
```

# Plotting Calculated Activated CD4 T cells

```{r}
library(ggplot2)
ActCD4 = read.csv('~/my.work/PhD/HomestaticExpansionProject/ModelData/ActivatedCD4pop.csv')
ggplot(ActCD4, aes(intage, CD4CT, colour=Genotype, fill=Genotype)) +
  geom_smooth(method="lm") +
  geom_point(size=3) +
  theme_bw() + 
  xlab("Age in Days") +
  ylab("CD4 T cell counts in 10^6") +
  ggtitle("Total CD4 T cells") + 
  expand_limits(y=0) +
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"),
        plot.title = element_text( size = 20, face = "bold")
        )
ggplot(ActCD4, aes(intage, ActivatedCD4CT, colour=Genotype, fill=Genotype)) +
  geom_smooth(method="lm") +
  geom_point(size=3) +
  theme_bw() + 
  xlab("Age in Days") +
  ylab("Activated CD4 T cell counts in 10^6") +
  ggtitle("Total Activated CD4 T cells") + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"),
        plot.title = element_text( size = 20, face = "bold")
        )

#Plots with sd need to be done on the summary results, so
library("Rmisc")
SumActivCD4 <- summarySE(ActCD4, measurevar="ActivatedCD4CT", groupvars=c("intage","Genotype"))

ggplot(SumActivCD4, aes(x=intage, y=ActivatedCD4CT, colour=Genotype, group=Genotype)) +
  geom_errorbar(aes(ymin=ActivatedCD4CT-se, ymax=ActivatedCD4CT+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Total CD4CD69+ Cells (10^6)", y = "Counts", x = "Age in Days") + 
  theme(axis.text=element_text(size=14), 
        axis.title=element_text(size=18,face="bold"), 
        plot.title = element_text( size = 20, face = "bold"))
```

#Regression Analysis of WT vs KO in CD4CD69+ T cells
```{r}
table(ActCD4$intage)
#ActCD4 
ActCD4WT = subset(ActCD4, Genotype == "WT")
ActCD4KO = subset(ActCD4, Genotype == "KO")

reg469WT = lm(formula = ActivatedCD4CT ~ intage, data = ActCD4WT)
reg469KO = lm(formula = ActivatedCD4CT ~ intage, data = ActCD4KO)
summary(reg469WT)
#Slope SE
#0.014052   0.003341
summary(reg469KO)
#0.05955    0.01007
#Calculating Z score (sl1 - sl2)/sqrt(SE1**2 + SE2**2)
(0.014052 - 0.05955) / sqrt(0.003341**2 + 0.01007**2)
#Z = -4.288312
#P =  0.000018
```
##Regression Analysis of WT vs KO in just CD4 T cells
```{r}
popNo56<-pop[!(pop$intage==56),]
popWT = subset(popNo56, Genotype == "WT")
popKO = subset(popNo56, Genotype == "KO")

reg4popWT = lm(formula = CD4CT ~ intage, data = popWT)
reg4popKO = lm(formula = CD4CT ~ intage, data = popKO)
summary(reg4popWT)
#Slope SE
#0.32875   0.06991
summary(reg4popKO)
#0.39749    0.07445
#Calculating Z score (sl1 - sl2)/sqrt(SE1**2 + SE2**2)
(0.32875 - 0.39749) / sqrt(0.06991**2 + 0.07445**2)
#Z = -0.6730743
#P =   .500947
```
#T test of day 12 WT vs KO
#T test on activated cd4 => 12
```{r}
ActCD4 = read.csv('~/my.work/PhD/Homestatic Expansion Project/ModelData/ActivatedCD4pop.csv')
d12WT = subset(ActCD4, intage == c(12,14, 18) & Genotype == "WT")
d12KO = subset(ActCD4, intage == c(12,14, 18) & Genotype == "KO")
dWT = d12WT$ActivatedCD4CT
dKO = d12KO$ActivatedCD4CT
t.test(dWT, dKO, alternative = "two.sided")
```
#T test on activated cd4 < 12
```{r}
ActCD4 = read.csv('~/my.work/PhD/Homestatic Expansion Project/ModelData/ActivatedCD4pop.csv')
d12WT = subset(ActCD4, intage < 12 & Genotype == "WT")
d12KO = subset(ActCD4, intage < 12 & Genotype == "KO")
dWT = d12WT$ActivatedCD4CT
dKO = d12KO$ActivatedCD4CT
t.test(dWT, dKO, alternative = "two.sided")
```

