---
title: "HomeostatPlots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Source for popcount
```{r}
#Preparing the data and the function
library(ggplot2)
library(scales)
```
Some info on the 'pop' dataset
- 1:18 - meta data associated with the experiment that generated the data
- 18:42 - Individual events counted/selected by the FCS express at the appropriate gate
- 43 - Age in integer format; Age(pop[,14]) is a column with the ages saved as factors for the purposes of creating the plots that I first made.
- 44+ - All calculations created from either 'popcount_V2.R' or this R script. E-mail jonazule@gmail.com if there is any confusion. 

#Plotting Thymus Weights
```{r}
pop = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/AfterCalculations.csv")
#Getting only the Thymus Weights
popThym = subset(pop, Organ == "Thymus")
#Making miligram
popThym$OrganWeight = popThym$OrganWeight * 100 
#Plotting the Thymus
ggplot(popThym, aes(intage, OrganWeight, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,56,4), limits = c(-0.8,56))+
  scale_y_continuous(breaks = seq(0,max(popThym$OrganWeight, na.rm = TRUE), 
                                  length.out =5), labels = label_number(accuracy = 0.11))+
  labs(titles = "Thymus Weight", x = "Age in Days", y = "Weight (milligram)")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/WithDay56/ThymusWeight.png",
       width = 7,
       height = 4)

#######################
#Excluding Adult sizes
#######################

popThymYoung = subset(popThym, intage < 40)
#MakingPlot
ggplot(popThymYoung, aes(intage, OrganWeight, shape = Genotype)) + 
  geom_point(position = position_dodge(0.5), size = 4)+
  scale_x_continuous(breaks = seq(0,18,2), limits = c(-0.8,18.5))+
  scale_y_continuous(breaks = seq(0,max(popThymYoung$OrganWeight, na.rm = TRUE), 
                                  length.out =5), labels = label_number(accuracy = 0.11))+
  labs(titles = "Thymus Weight", x = "Age in Days", y = "Weight (milligram)")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
        legend.key = element_rect(fill = "white", colour = "black"),
        legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/ThymusWeight.png",
       width = 5.5,
       height = 4)

popThym18WT = subset(popThym, intage == 18 & Genotype == "WT")
popThym18KO = subset(popThym, intage == 18 & Genotype == "KO")
t.test(popThym18WT$OrganWeight, popThym18KO$OrganWeight)
```
# Spleen Weight
```{r}
pop = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/AfterCalculations.csv")

#####################
#     SPLEEN
#####################

popSpln = subset(pop, Organ == "Spleen")
#Making the data in milligrams
popSpln$OrganWeight = popSpln$OrganWeight * 100 
#removing the day 56 outlier
popSpln = subset(popSpln, OrganWeight < 75)
#Plotting the Thymus
ggplot(popSpln, aes(intage, OrganWeight, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,56,4))+
  labs(titles = "Spleen Weight", x = "Age in Days", y = "Weight (milligram)")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/WithDay56/SpleenWeight.png",
       width = 7,
       height = 4)

#Excluding Adult sizes
popSplnYoung = subset(popSpln, intage < 40)

#MakingPlot
ggplot(popSplnYoung, aes(intage, OrganWeight, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,18,2), limits = c(-0.5,18.5))+
  labs(titles = "Spleen Weight", x = "Age in Days", y = "Weight (milligram)")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
        legend.key = element_rect(fill = "white", colour = "black"),
        legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/SpleenWeight.png",
       width = 5.5,
       height = 4)
```

#Naive T Cells Spleen
```{r}
ActivationData = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/ActivatedCD4pop.csv")

#Changing total cell count to 10**6
ActivationData$NaiveCT = ActivationData$NaiveCT * 10**6
ggplot(ActivationData, aes(intage, NaiveCT, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,18,2))+
  scale_y_continuous(breaks = seq(0,max(ActivationData$NaiveCT), length.out = 5), labels =label_scientific(digits = 2) )+
  labs(titles = "Naive T Cell Total Count", x = "Age in Days", y = "CD4+TCRbeta_high-CD69-Foxp3-")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 18),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/NaiveTCell_Count.png",
       width = 5.5,
       height = 4)
```
# Treg Plots With Day 56
```{r}

pop = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/AfterCalculations.csv")
#removing an outlier and Day 0
TregData = subset(pop, X4TregCT < 1 & intage > 0)
#Making converting the x4Treg values to millions
TregData$X4TregCT = TregData$X4TregCT *10**6
ggplot(TregData, aes(intage, X4TregCT, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 3)+
  scale_x_continuous(breaks = seq(4,56,4))+
  scale_y_continuous(breaks = seq(0,max(TregData$X4TregCT), length.out =5), 
                     labels = scientific_format(digits = 2))+
  labs(titles = "Treg Total count", x = "Age in Days", y = "CD4+Foxp3+TCRbeta_high Count")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 18),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/WithDay56/Treg_Count.png",
       width = 7,
       height = 4)

##############
#
#   Treg Percentage
#
##############

ggplot(TregData, aes(intage, X4TregRatio, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(4,56,4))+
  scale_y_continuous(breaks = seq(0,max(TregData$X4TregRatio), length.out = 5),
                     labels = label_percent())+
  labs(titles = "Treg Percentage", x = "Age in Days", y = "CD4+Foxp3+TCRbeta_high Percentage")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 15),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/WithDay56/Treg_Pct.png",
       width = 7,
       height = 4)

```
# Treg Plots Young
```{r}
pop = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/AfterCalculations.csv")
#removing an outlier, Day 0, and Day 56
TregData = subset(pop, X4TregCT < 1 & intage > 0 & intage < 50)
TregData$X4TregCT = TregData$X4TregCT *10**6
ggplot(TregData, aes(intage, X4TregCT, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(4,18,2))+
  scale_y_continuous(breaks = seq(0,max(TregData$X4TregCT), length.out =5),
                     labels = scientific_format(digits = 2))+
  labs(titles = "Treg Total count", x = "Age in Days", y = "CD4+Foxp3+TCRbeta_high Count ")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 18),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/Treg_Count.png",
       width = 5.5,
       height = 4)

##############
#
#   Treg Percentage
#
##############

ggplot(TregData, aes(intage, X4TregRatio, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(4,18,2))+
  scale_y_continuous(breaks = seq(0,max(TregData$X4TregRatio), length.out = 5),
                     labels = label_percent())+
  labs(titles = "Treg Percentage", x = "Age in Days", y = "CD4+Foxp3+TCRbeta_high Percentage")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 16),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/Treg_Pct.png",
       width = 5.5,
       height = 4)
```
#Activated T Cell Plots
```{r}
ActivationData = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/ActivatedCD4pop.csv")
ActivationData$ActivatedCD4CT =ActivationData$ActivatedCD4CT * 10**6
ggplot(ActivationData, aes(intage, ActivatedCD4CT, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks =seq(0,18,2))+
  scale_y_continuous(breaks = seq(0, max(ActivationData$ActivatedCD4CT), 
                                  length.out = 5), 
                     labels =  label_scientific(digits = 2))+
  labs(titles = "Activated T Cell Total Count", x = "Age in Days", y = "CD4+CD69+ Count")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/ActivatedTCells.png",
       width = 5.5,
       height = 4)
```
#CD69 Percentage
```{r}
CD69Data = read.csv('~/my.work/PhD/HomestaticExpansionProject/ModelData/CD69DataFromGen.csv')
#Removing day 0, because it is always weird
CD69Data = subset(CD69Data, Age > 0)
CD69Data$CD4CD69_pct = CD69Data$CD4CD69_pct / 100
ggplot(CD69Data, aes(Age, CD4CD69_pct, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(4,20,2))+
  scale_y_continuous(breaks = seq(0,max(CD69Data$CD4CD69_pct, na.rm = TRUE),
                                  length.out =5),
                     labels = label_percent())+
  labs(titles = "Activated T Cell Percentage", x = "Age in Days", y = "CD4+CD69+ Count")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/CD69_Pct.png",
       width = 5.5,
       height = 4)

```
# CD44+CD62L+
```{r}
CD69Data = read.csv('~/my.work/PhD/HomestaticExpansionProject/ModelData/CD69DataFromGen.csv')
CD69Data = subset(CD69Data, Age > 0)
CD69Data$CD4CD44CD62L_pct = CD69Data$CD4CD44CD62L_pct /100
ggplot(CD69Data, aes(Age, CD4CD44CD62L_pct, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks =seq(4,19,2))+
  scale_y_continuous(breaks = seq(0,max(CD69Data$CD4CD44CD62L_pct, na.rm = TRUE),
                                  length.out =5),
                     labels = label_percent())+
  labs(titles = "CD4CD44CD62L+ Percentage", x = "Age in Days", y = "CD4CD44CD62L+ Percentage")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/CD44CD62.png",
       width = 5.5,
       height = 4)

```
#Plotting Naive and Thymus Derived Tregs
```{r}
dfTreg = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/ActivatedCD4pop.csv")
#Converting to Millions
dfTreg$NaiveDerivedTregsCT = dfTreg$NaiveDerivedTregsCT * 10**6
dfTreg$X4TregFromThymusCT = dfTreg$X4TregFromThymusCT * 10**6
dfTreg$AllTregs = dfTreg$AllTregs * 10**6

#Naive Derived
ggplot(dfTreg, aes(intage, NaiveDerivedTregsCT, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,18,2))+
  scale_y_continuous(breaks = seq(0,max(dfTreg$NaiveDerivedTregsCT), length.out =5),
                     labels = scientific_format(digits = 2))+
  labs(titles = "Naive Derived Tregs", x = "Age in Days", y = "CD4+Foxp3+ Count")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/NaiveDerivedTregs.png",
       width = 5.5,
       height = 4)
#Thymus Derived
ggplot(dfTreg, aes(intage, X4TregFromThymusCT, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,18,2))+
  scale_y_continuous(breaks = seq(0,max(dfTreg$X4TregFromThymusCT), length.out =5),
                     labels = scientific_format(digits = 2))+
  labs(titles = "Thymus Derived Tregs", x = "Age in Days", y = "CD4+Foxp3+ Count")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/ThymusDerivedTregs.png",
       width = 5.5,
       height = 4)

#All Tregs
ggplot(dfTreg, aes(intage, AllTregs, shape = Genotype)) + 
  geom_point(position = position_dodge(1), size = 4)+
  scale_x_continuous(breaks = seq(0,18,2))+
  scale_y_continuous(breaks = seq(0,max(dfTreg$AllTregs), length.out =5),
                     labels = scientific_format(digits = 2))+
  labs(titles = "Naive + Thymus Derived Tregs", x = "Age in Days", y = "CD4+Foxp3+ Count")+
  theme(panel.background = element_rect(fill = "white", colour = "black", size = 2),
                 legend.key = element_rect(fill = "white", colour = "black"),
                 legend.background = (element_rect(colour= "black", fill = "white")),
        axis.title.x = element_text(face="bold", colour="black", size=20),
        axis.title.y = element_text(face = "bold", colour = "black", size = 20),
        plot.title = element_text(lineheight=.8, face="bold", size = 20),
        axis.ticks.length=unit(.25, "cm"),
        text = element_text(size=20))+
  stat_summary(aes(group=Genotype, color = Genotype), fun.y=mean, geom="line")
ggsave("~/my.work/PhD/HomestaticExpansionProject/Plots/HomeoPlots/Young/AllTregs.png",
       width = 5.5,
       height = 4)
```

# Calculating Treg Frequency that did not come from Thymus
```{r}
pop = read.csv("~/my.work/PhD/HomestaticExpansionProject/ModelData/AfterCalculations.csv")
library(dplyr)
library("Rmisc")
library("reshape2")
#Need to remove dates that are not symmetrical for subtractions - Dates are 2/25/2018 and 12/6/2017
#There is a missing thymus and only one thymus for one of the dates - Incomplete data

popNoInc <- pop[!(pop$intage == 18 & pop$expDate=="2/25/2018" | pop$expDate=="12/6/2017"),]
#day 0 screwing with the data
popNoInc = popNoInc[!(popNoInc$Age == "0"),]
#A d56 spleen doesn't have a thymus partner
popNoInc = popNoInc[!(popNoInc$FileID == "JA022518WK8M1WTS"),]

################################3
# Testing
popTest = subset(popNoInc, intage == 12, select = c(Genotype, intage, Organ, X4TregRatio, expDate))
#0.070089650 - 0.015605014 = 0.05448464 0.05448464
#WT 10/25 spleen - this should be the result
popTest = popTest %>%
   group_by(intage, Genotype, expDate) %>% #expDate is to subtract only by the thymus from the same experiment
   mutate(NaiveDerivedTregs = X4TregRatio - X4TregRatio[Organ == 'Thymus'])
View(popTest)
#
################################

#Grouping and then subtracting Thymus treg freq from Spleen
popNoInc = popNoInc %>%
   group_by(Age, Genotype, expDate) %>% #expDate is to subtract only by the thymus from the same experiment
   mutate(Diff = X4TregRatio - X4TregRatio[Organ == 'Thymus'])
#Tregs derived from the Thymus
popNoInc$X4TregFromThymus = popNoInc$X4TregRatio - popNoInc$Diff
#Replacing the Negative Values with 0
popNoInc$Diff[popNoInc$Diff < 0] <- 0

#plotting differences

#Removing the same things from the original file as I did for the popNoInc
pop2 <- pop[!(pop$intage == 18 & pop$expDate=="2/25/2018" | pop$expDate=="12/6/2017"),]
#day 0 screwing with the data
pop2 = pop2[!(pop2$Age == "0"),]
#A d56 spleen doesn't have a thymus partnet
pop2 = pop2[!(pop2$FileID == "JA022518WK8M1WTS"),]

pop2S = subset(pop2, Organ == "Spleen")
popNoIncS = subset(popNoInc , Organ == "Spleen")

ggplot(pop2S, aes(x=Age, y=X4TregRatio, colour=Genotype, group=Genotype)) +
  geom_point(size=3) +
  labs(title = "Tregulatory Cell Frequencies from the Spleen",
       y = "Treg Percentages")+
  ylim(0, 0.175)

# Treg with error bars
TregError <- summarySE(pop2S, measurevar="X4TregRatio", groupvars=c("Age","Genotype"))
#Replacing the NA's produced by day 1's
TregError[is.na(TregError)] = 0
ggplot(TregError, aes(x=Age, y=X4TregRatio, colour=Genotype, group=Genotype)) + 
  geom_errorbar(aes(ymin=X4TregRatio-se, ymax=X4TregRatio+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Treg Population Percentage in the Spleen", y = "Percent", x = "Age in Days")+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=18,face="bold"),
        plot.title = element_text( size = 15, face = "bold")
        )

ggplot(popNoIncS, aes(x=Age, y=Diff, colour=Genotype, group=Genotype)) + 
  geom_point(size=3)+
  labs(title = "Minus the Thymus Frequencies", 
       y = "Treg Frequency Minus Thymus Frequency")+
  ylim(0, 0.175)
ggplot(popNoIncS, aes(x=Age, y=X4TregFromThymus, colour=Genotype, group=Genotype)) + 
  geom_point(size=3)+
  labs(title = "Treg Frequencies from Thymus", 
       y = "Frequencies from Thymus")+
  ylim(0, 0.175)

```






