---
title: "R Notebook"
output: html_notebook
---
```{r}
#Preparing the data and the function
source('~/my.work/PhD/Homestatic Expansion Project/Code/Rscripts/popCount_V2.R')
library(ggplot2)
```

Some info on the 'pop' dataset
- 1:18 - meta data associated with the experiment that generated the data
- 18:42 - Individual events counted/selected by the FCS express at the appropriate gate
- 43 - Age in integer format; Age(pop[,14]) is a column with the ages saved as factors for the purposes of creating the plots that I first made.
- 44+ - All calculations created from either 'popcount_V2.R' or this R script. E-mail jonazule@gmail.com if there is any confusion. 

#Doing t tests on the ages
```{r}
#Functions
ageTtest = function(column){
  age = c(0,4,7,9,12,14,18)
  results = data.frame(matrix(ncol = 2, nrow = 0))
  colnames(results) <- c("Age", "Pvalue")
  #Do not change the name of pop dataframe in popCount_V2.R script
  for (i in age){
    wt = subset(pop, intage == i & Genotype == "WT", select = column)
    ko = subset(pop, intage == i & Genotype == "KO", select = column)
    tt = t.test(wt, ko, alternative = "two.sided")
    results[nrow(results)+1,] <- c(i, tt$p.value)
  }
  return(results)
}

```

```{r}
#T test bulk ages
BulkTestWithAgeCutoff = function(column, age, lessOrGreater = "Greater"){
  #data will always be pop
  # ages are age = c(0,4,7,9,12,14,18)
  if (lessOrGreater == "less"){
    wt = subset(pop, intage <= age & Genotype == "WT")
    ko = subset(pop, intage <= age & Genotype == "KO")
  } else {
    wt = subset(pop, intage >= age & Genotype == "WT" & intage < 56 )
    ko = subset(pop, intage >= age & Genotype == "KO" & intage < 56)
  }
  results = t.test(wt[[column]], ko[[column]], alternative = "two.sided")
  return(results)
}
```

```{r}
ageTtest("CD4CT")
ageTtest("CD4Ratio")
ageTtest("Bratio")
ageTtest("CD4ProlCT")
ageTtest("X4TregRatio")
ageTtest("CD8ct")
```

```{r}
#Pulling out the counts that were not proliferating
pop$CD4nonProliferating_CT = pop$CD4CT - pop$CD4ProlCT
ageTtest("CD4nonProliferating_CT")
```

```{r}
#Looking to see the ratio of non activated
pop$CD4nonProliferating_Ratio = pop$CD4nonProliferating_CT/pop$CD4CT
summary(pop$CD4nonProliferatingd_Ratio)
hist(pop$CD4nonProliferating_Ratio, breaks = seq(0,1,0.01))
lowFreq = subset(pop, CD4nonProliferating_Ratio <= 0.5)
highFreq = subset(pop, CD4nonProliferating_Ratio >= 0.5)
hist(lowFreq$intage)
hist(highFreq$intage)

#We have a high number of non activation in the ages above 10
```

```{r}
#High non activation difference between WT and KO
#High numbers of non activated cells
highNonProlWT = subset(pop, CD4nonProliferating_Ratio >= 0.5 & Genotype == "WT")
highNonProlKO = subset(pop, CD4nonProliferating_Ratio >= 0.5 & Genotype == "KO")
par(mfrow=c(1,2))
hist(highNonProlKO$intage, main = "HignNonProl KO")
hist(highNonProlWT$intage, main = "HignNonProl WT")
t.test(highNonProlWT$CD4nonActivated_Ratio, highNonProlKO$CD4nonActivated_Ratio, alternative = "two.sided")

# ageTtest("CD4nonActivated_Ratio")

```

```{r}
#Testing to see proliferation
hist(pop$CD4ProlRatio, main = "Proliferation of All")
highProlWT =  subset(pop, CD4ProlRatio >= 0.5 & Genotype == "WT")
highProlKO =  subset(pop, CD4ProlRatio >= 0.5 & Genotype == "KO")
par(mfrow=c(1,2))
hist(highProlWT$intage, main = "HighProl CD4 KO")
hist(highProlKO$intage, main = "HignProl CD4 WT")
t.test(highProlWT$CD4ProlRatio, highProlKO$CD4ProlRatio, alternative = "two.sided")
t.test(highFreqWT$CD4nonActivated_Ratio, highFreqKO$CD4nonActivated_Ratio, alternative = "two.sided")
```
```{r}
#Testing the proliferation of CD4s of ages 9 and above
prol9nGreaterWT = subset(pop, intage >= 9 & Genotype == "WT" & intage < 56 )
prol9nGreaterKO = subset(pop, intage >= 9 & Genotype == "KO" & intage < 56 )
t.test(prol9nGreaterWT$CD4ProlRatio, prol9nGreaterKO$CD4ProlRatio, alternative =  "two.sided")
```
```{r}
BulkTestWithAgeCutoff("CD4ProlRatio",9)
BulkTestWithAgeCutoff("X4TregRatio",9)
ageTtest("X4TregRatio")
#Tregs have a statistical differences when it comes to age by age at age 9 and 4, and almost at day 19
#When bulked all treg ratio numbers above age 9 are statistically significant
```

#Checking Weights of Organs and Mice
```{r}
#Checking out the Spleen and Thymus Weights
ThymWeight = subset(pop, Organ == "Thymus")
SplnWeightKO = subset(pop, Organ == "Spleen" & OrganWeight < 0.79 & Genotype == "KO")
SplnWeightWT = subset(pop, Organ == "Spleen" & OrganWeight < 0.79 & Genotype == "WT")
#There is an outlier in the spleen weight
SplnWeight 
plot(ThymWeight$Age,ThymWeight$OrganWeight)
plot(SplnWeight$Age, SplnWeight$OrganWeight)
plot(SplnWeightKO$Age, SplnWeightKO$OrganWeight)
plot(SplnWeightWT$Age, SplnWeightWT$OrganWeight)

#plot the cell counts
#
```

```{r}
#Using GGplot to check out the weights
ggplot(data=SplnWeight, aes(x=Age, y=OrganWeight)) +
  geom_point(position = position_dodge(width = 0.8), aes(color = Genotype))
  
ggplot(data=ThymWeight, aes(x=Age, y=OrganWeight)) +
  geom_point(position = position_dodge(width = 0.8), aes(color = Genotype))
  
```


####################################
#Getting Treg values that did not come from the thymus
```{r}
#Plotting and Continuously working with data
source("~/my.work/PhD/Homestatic Expansion Project/Code/Rscripts/popCount_V2.R")
source("~/my.work/PhD/Homestatic Expansion Project/Code/Rscripts/FunctionsData.R")
library(dplyr)
library("Rmisc")
library("reshape2")
#Need to remove dates that are not symmetrical for subtractions - Dates are 2/25/2018 and 12/6/2017
#There is a missing thymus and only one thymus for one of the dates - Incomplete data

popNoInc <- pop[!(pop$intage == 18 & pop$expDate=="2/25/2018" | pop$expDate=="12/6/2017"),]
#day 0 screwing with the data
popNoInc = popNoInc[!(popNoInc$Age == "0"),]
#A d56 spleen doesn't have a thymus partner
popNoInc = popNoInc[!(popNoInc$FileID == "JA022518WK8M1WTS"),]
#Grouping and then subtracting Thymus treg freq from Spleen
popNoInc = popNoInc %>%
   group_by(Age, Genotype, expDate) %>%
   mutate(Diff = X4TregRatio - X4TregRatio[Organ == 'Thymus'])
#Values removed by Thymus
popNoInc$X4TregFromThymus = popNoInc$X4TregRatio - popNoInc$Diff
#Replacing the Negative Values with 0
popNoInc$Diff[popNoInc$Diff < 0] <- 0

#plotting differences

#Removing the same things from the original file as I did for the popNoInc
pop2 <- pop[!(pop$intage == 18 & pop$expDate=="2/25/2018" | pop$expDate=="12/6/2017"),]
#day 0 screwing with the data
pop2 = pop2[!(pop2$Age == "0"),]
#A d56 spleen doesn't have a thymus partnet
pop2 = pop2[!(pop2$FileID == "JA022518WK8M1WTS"),]

pop2S = subset(pop2, Organ == "Spleen")
popNoIncS = subset(popNoInc , Organ == "Spleen")

ggplot(pop2S, aes(x=Age, y=X4TregRatio, colour=Genotype, group=Genotype)) +
  geom_point(size=3) +
  labs(title = "Tregulatory Cell Frequencies from the Spleen",
       y = "Treg Percentages")+
  ylim(0, 0.175)

# Treg with error bars
TregError <- summarySE(pop2S, measurevar="X4TregRatio", groupvars=c("Age","Genotype"))
#Replacing the NA's produced by day 1's
TregError[is.na(TregError)] = 0
ggplot(TregError, aes(x=Age, y=X4TregRatio, colour=Genotype, group=Genotype)) + 
  geom_errorbar(aes(ymin=X4TregRatio-se, ymax=X4TregRatio+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Treg Population Percentage in the Spleen", y = "Percent", x = "Age in Days")+
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=18,face="bold"),
        plot.title = element_text( size = 20, face = "bold")
        )

ggplot(popNoIncS, aes(x=Age, y=Diff, colour=Genotype, group=Genotype)) + 
  geom_point(size=3)+
  labs(title = "Minus the Thymus Frequencies", 
       y = "Treg Frequency Minus Thymus Frequency")+
  ylim(0, 0.175)
ggplot(popNoIncS, aes(x=Age, y=X4TregFromThymus, colour=Genotype, group=Genotype)) + 
  geom_point(size=3)+
  labs(title = "Treg Frequencies from Thymus", 
       y = "Frequencies from Thymus")+
  ylim(0, 0.175)

```

#Plotting Thymus weights between Wt KO

```{r}
popThym = subset(pop, Organ == "Thymus")
ggplot(popThym, aes(x=Age, y=OrganWeight, colour=Genotype, group=Genotype)) + 
  geom_point(size=3)+
  theme_bw() + 
  xlab("Age in Days") +
  ylab("Activated CD4 T cell counts in 10^6") +
  ggtitle("Total Activated CD4 T cells") + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"),
        plot.title = element_text( size = 20, face = "bold")
        )

outlier = subset(popThym, OrganWeight > 0.24)
```





#Comparing regression of two different trend lines

```{r}
####################################
#
#Relevant information:
#PAPERS
#Papers that go over how to choose the right methods
#     1- Paternoster, R., Brame, R., Mazerolle, P., & Piquero, A. R. (1998). Using the Correct Statistical Test for the Equality of Regression Coefficients. Criminology, 36(4), 859–866.
#     2- Andrade, J. M., and M. G. Estévez-Pérez. "Statistical comparison of the slopes of two regression lines: A tutorial." Analytica chimica acta 838 (2014): 1-12.
#
#LINK TO BEST HELP
#https://stats.stackexchange.com/questions/55501/test-a-significant-difference-between-two-slope-values

# Link that goes over the different ways to make sure your calculations are right
####################################

```

```{r}
#Actually calculating the regression lines and getting p values
source("~/my.work/PhD/Homestatic Expansion Project/Code/Rscripts/popCount_V2.R")
#Subsetting WT and KO - Removing the ones older than 56 because those we are not considering
popWT = subset(pop, Genotype == "WT" & intage < 56)
popKO = subset(pop, Genotype == "KO")
#Independent variable is age, and we are trying to predict CD4CT (dependent)
regWT = lm(formula = CD4CT ~ intage, data = popWT)
regKO = lm(formula = CD4CT ~ intage, data = popKO)
summary(regWT)
#CD4CT ~ intage - 0.32875, 0.06991
summary(regKO)
#CD4CT ~ intage - 0.39749, 0.07445
#Calculating Z score (sl1 - sl2)/sqrt(SE1**2 + SE2**2)
(0.32875 - 0.39749) / sqrt(0.06991**2 + 0.07445**2)
#Z = -0.6730743
#p-value - 0.250474
```

```{r}
#Visualizing the trend lines
ggplot(popWT, aes(x=intage, y=CD4CT)) +
  geom_point(shape=1) +    # Use hollow circles
  geom_smooth(method=lm) +  # Add linear regression line
  labs(title = "Wild Type CD4 counts, slope = 0.8722") #(by default includes 95% confidence region)
ggplot(popKO, aes(x=intage, y=CD4CT)) +
  geom_point(shape=1) +    # Use hollow circles
  geom_smooth(method=lm)+   # Add linear regression line 
  labs(title = "Knock Out CD4 counts, slope = 0.8587")  #  (by default includes 95% confidence region)

```
```{r}
#Trend lines of the CD4 frequencies

regrWT = lm(formula = CD4Ratio ~ intage, data = popWT)
regrKO = lm(formula = CD4Ratio ~ intage, data = popKO)
summary(regrWT)
summary(regrKO)
```


```{r}
#visualizing trend lines of frequencies
ggplot(popWT, aes(x=intage, y=CD4Ratio)) +
  geom_point(shape=1) +    # Use hollow circles
  geom_smooth(method=lm) +  # Add linear regression line
  labs(title = "Wild Type CD4 counts, slope = ") #(by default includes 95% confidence region)
ggplot(popKO, aes(x=intage, y=CD4Ratio)) +
  geom_point(shape=1) +    # Use hollow circles
  geom_smooth(method=lm)+   # Add linear regression line 
  labs(title = "Knock Out CD4 counts, slope = ")  #  (by default includes 95% confidence region)
```


```{r}
popSpln = subset(pop, Organ == "Spleen")
pop$TotalLiveCountInMillions
pd <- position_dodge(0.1)
ggplot(popSpln, aes(x=Age, y=TotalLiveCountInMillions, colour=Genotype, group=Genotype)) + 
  geom_point(position=pd, size=3) +
  labs(title = "Total CD4 T Cell Counts in the 10^6", y = "Counts", x = "Age in Days")

#get total splenic cell counts for WT and KO up to 4 each from Genevieve and Kristen.
```





#Plotting CD4 T cells all ages, pre 12, post 9
```{r}
#Guide I am using - http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/
#Now to get the error bars
source("~/my.work/PhD/Homestatic Expansion Project/Code/Rscripts/popCount_V2.R")
library("Rmisc")
SpleenOnly = subset(pop, Organ == "Spleen")
CD4ct <- summarySE(SpleenOnly, measurevar="CD4CT", groupvars=c("Age","Genotype"))

ggplot(CD4ct, aes(x=Age, y=CD4CT, colour=Genotype, group=Genotype)) + 
  geom_errorbar(aes(ymin=CD4CT-se, ymax=CD4CT+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Total CD4 T Cells in the 10^6 with SE bars", y = "Counts", x = "Age in Days") + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=18,face="bold"),
        plot.title = element_text( size = 20, face = "bold"))

SpleenPre12 <- subset(SpleenOnly, intage < 12)
CD4ctpre12 <- summarySE(SpleenPre12, measurevar="CD4CT", groupvars=c("Age","Genotype"))
ggplot(CD4ctpre12, aes(x=Age, y=CD4CT, colour=Genotype, group=Genotype)) + 
  geom_errorbar(aes(ymin=CD4CT-se, ymax=CD4CT+se), colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd, size=3) +
  labs(title = "Total CD4 T Cells in the 10^6 with SE bars", y = "Counts", x = "Age in Days") + 
  theme(axis.text=element_text(size=14),
        axis.title=element_text(size=18,face="bold"),
        plot.title = element_text( size = 20, face = "bold"))

```










